---
title: "final test"
author: "Troy Zhou"
output: github_document
---

```{r load_package, echo = FALSE, message=FALSE}
library(tidyverse)
options(tibble.print_min = 5)
options(pillar.sigfig = 5)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

```

## load state people wearing mask last 5 days 

```{r}

mask_5d <- read.csv("data/covidcast-fb-survey-smoothed_wwearing_mask-2021-01-01-to-2022-11-27.csv")

count_table<-mask_5d %>% group_by(geo_value) %>% 
  summarize(count=n()) %>% 
  knitr::kable(digits = 2)

# test_df<-mask_5d %>% nest_by(geo_value)
mask_5d[1:5,]

```

* variable list ``r colnames(mask_5d)`` 

* long format with state code and all dates

## load state people wearing mask last 5 days unweighted

```{r}
mask_5d_unweighted <- read.csv("data/covidcast-fb-survey-smoothed_wearing_mask-2021-01-01-to-2022-11-27.csv")
```

Sampling weights are non-negative values associated with survey responses that 
usually exist in any publicly available survey data. Sampling weights are supposed to 
be inversely proportional to the selection probabilities of sample units in the target 
population, whose main goal is to improve the representativeness of the sample with 
respect to a target population. Naive analyses of the data under a complex sample 
design are expected to result in biased estimates. For instance, unweighted inference 
based on CTIS data tends to overestimate vaccination rates among adult Facebook 
users. In the following section, we further explain why it is necessary to use the 
sampling weights in our statistical analysis


